Test data

### 2022-07-19 Shiny/Test/Flexdashboard rows.Rmd
Improved value boxes. Annual result plot.

### ggplot
```{r}
plotOutput("htmlplot")
```

@@

    # Creating KPI_admin value
    KPI_admin <- reactive({exceldata() |> 
           mutate(
      KPI_admin =
        str_c( # Using str_c() to concatenate value and % sign
         format( # shortening(lengthening) the resulting value
           # calculating the value
          (expenses_administrative / expenses_program_services *100), digits = 3
          ), "%"
         )
      ) |> 
      filter(year == max(year)) |> # selecting latest available year
       select(KPI_admin) |> # dropping all other variables
        str_flatten() # turning into a single string
         })

    # Creating the first value box
    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "primary",
        color = "primary",
        icon = "fa-random"
        )
      })

    # Duplicate value boxes for testing
    output$KPI_box2 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "danger",
        color = "danger",
        icon = "fas fa-dog"
      )

    })
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "success",
        color = "success",
        icon = "fas fa-coffee"
      )
    })

@@

    # fancier plot function
    fancyplot <- reactive(
      htmldata() |> 
        select(
          year, lederlonn, leder_annen_godtgjorelse
         ) |> 
        rename( # renaming for the purposes of the plot
          Year = year,
          Salary = lederlonn,
          `Other compensation` = leder_annen_godtgjorelse
        ) |> 
        # pivoting to join the two values to use fill
        pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
        ggplot(aes(Year, value, fill = Compensation)) +
        geom_col() +
        scale_y_continuous(
          # Checking for uniform currency code
        labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
         ) +
        scale_fill_met_d("Troy") + # pretty colours
        labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(htmldata()$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
        )

  # Creating fancy plotlyplot
    fancyplotly <- reactive({
      ggplotly(fancyplot())
    })

  # Creating fancy plotly output  
    output$fancyplotly <- renderPlotly(
      fancyplotly()
    )
})

>>>>

### Annual result
```{r}
plotlyOutput("arsresultat_plot")
```

@@

    # Creating KPI_admin value
    KPI_admin <- reactive({
      exceldata() |> 
           mutate(
      KPI_admin =
        str_c( # Using str_c() to concatenate value and % sign
         format( # shortening(lengthening) the resulting value
           # calculating the value
          (expenses_administrative / expenses_program_services *100), digits = 3
          ), "%"
         )
      ) |> 
      filter(year == max(year)) |> # selecting latest available year
       select(KPI_admin) |> # dropping all other variables
        str_flatten() # turning into a single string
         })

    # Creating Fundraising ROI value
    KPI_fundraising_num <- reactive({
      exceldata() |> 
          mutate(
            # Calculating the value as a percentage
            KPI_fundraising_num =
              (revenue_private_contributions +
                 revenue_membership_fees - expenses_fundraising) /
              expenses_fundraising * 100) |> 
        # most recent year
          filter(year == max(year)) |> 
        # just want the single number
          select(KPI_fundraising_num) |> 
          pull()
    })

    # Creating the value box for administrative expenses
    output$KPI_box <- renderValueBox({
      valueBox(
        value = KPI_admin(),
        caption = "Admin spend",
        color = "primary",
        icon = "fa-random"
        )
      })

    # Creating value box for fundraising ROI
      # Unsure about colour levels
    output$KPI_box2 <- renderValueBox({
      valueBox(
        # shortening(lengthening) the value with format()
        # Using str_c() to concatenate value and % sign;
        value = str_c(format(KPI_fundraising_num(), digits = 3), "%"),
        caption = "Fundraising ROI",
        # Colour depends on value
        color = if (KPI_fundraising_num() < 100) {"danger"
          } else if (KPI_fundraising_num() < 200) {"warning"
            } else {"success"},
        icon = "fas fa-donate"
      )
    })

    # Duplicate value boxes for testing
    output$KPI_box3 <- renderValueBox({
      valueBox(
        value = str_c(format(KPI_fundraising_num(), digits = 3), "%"),
        caption = "success",
        color = "success",
        icon = "fas fa-coffee"
      )
    })

@@

    # fancier plot function
    fancyplot <- reactive(
      htmldata() |> 
        select(
          year, lederlonn, leder_annen_godtgjorelse
         ) |> 
        # renaming for the purposes of the plot
        rename( 
          Year = year,
          Salary = lederlonn,
          `Other compensation` = leder_annen_godtgjorelse
        ) |> 
        # pivoting to join the two values to use fill
        pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |> 
        ggplot(aes(Year, value, fill = Compensation)) +
        geom_col() +
        scale_y_continuous(
          # Checking for uniform currency code
        labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
         ) +
        # pretty colours
        scale_fill_met_d("Troy") + 
        labs(x = "Year", y = "Total compensation", title = "Annual CEO compensation",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(htmldata()$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
        )

  # Creating fancy plotly output  
    output$fancyplotly <- renderPlotly(
      ggplotly(fancyplot())
    )

# Creating plots - annual result
    arsresultat_plot <- reactive({
      htmldata() |> 
      mutate(
        profit = ifelse(arsresultat >= 0, TRUE, FALSE)
      ) |> 
      ggplot(aes(year, arsresultat, fill = profit)) +
      geom_col() +
      scale_y_continuous(
        labels = ifelse(length(unique(htmldata()$valutakode)) == 1,
                        # Using the currency code if uniform
                    label_dollar(prefix = str_c(htmldata()$valutakode[1], " ")),
                        # alternative prefix if multiple currencies in the data
                    label_dollar(prefix = "? "))
        ) +
      scale_fill_met_d("Tsimshian") +
      theme(legend.position = "none") +
      labs(x = "Year", y = "", title = "Annual result",
             # Checking again for currency; including warning if not uniform
        subtitle = ifelse(length(unique(htmldata()$valutakode)) == 1,
                         "",
                         "Note: not all values are denominated in the same currency"))
    })

    output$arsresultat_plot <- renderPlotly(
      ggplotly(arsresultat_plot())
    )

})
```

### 2022-07-19 Shiny/Test/Test data.Rmd
Improved value boxes. Annual result plot.

arsresultat_p_met <- kreft_html |> 
  mutate(
    profit = ifelse(arsresultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, arsresultat, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  scale_fill_met_d("Tsimshian")
ggplotly(arsresultat_p_met)

@@

ordinaert_p_met <- kreft_html |> 
  mutate(
    profit = ifelse(ordinaert_resultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, ordinaert_resultat, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  theme(legend.position = "none") +
  scale_fill_met_d("Tsimshian")
ggplotly(ordinaert_p_met)
```

@@

kreft_excel |> 
  mutate(
    KPI_admin =
      str_c(
        format(
        ((revenue_private_contributions +                  revenue_membership_fees) / expenses_fundraising * 100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()

>>>>

arsresultat_p_met <- kreft_html |> 
  mutate(
    profit = ifelse(arsresultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, arsresultat, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  scale_fill_met_d("Tsimshian") +
  theme(legend.position = "none")
ggplotly(arsresultat_p_met)

@@

ordinaert_p_met <- kreft_html |> 
  mutate(
    profit = ifelse(ordinaert_resultat >= 0, TRUE, FALSE)
  ) |> 
  ggplot(aes(year, ordinaert_resultat, fill = profit)) +
  geom_col() +
  scale_y_continuous(labels = scales::label_dollar(prefix = "")) +
  theme(legend.position = "none") +
  scale_fill_met_d("Tsimshian") +
  theme(legend.position = "none") +
  labs(x = "", y = "")
ggplotly(ordinaert_p_met)
```

@@

# Numeric, for further transformation

KPI_fundraising_num <- kreft_excel |> 
          mutate(
            KPI_fundraising_num =
              (revenue_private_contributions +
                 revenue_membership_fees - expenses_fundraising) /
              expenses_fundraising * 100) |> 
  filter(year == max(year)) |> 
  select(KPI_fundraising_num) |> 
  pull()

# To turn into percentage
str_c(format(KPI_fundraising_num, digits = 3), "%")

KPI_fundraising_num

if (KPI_fundraising_num < 100) {"danger"} else if (KPI_fundraising_num < 200) {"warning"} else {"success"}

kreft_excel |> 
  mutate(
    KPI_admin =
      str_c(
        format(
        ((revenue_private_contributions + revenue_membership_fees - expenses_fundraising) / expenses_fundraising * 100), digits = 3
        ), "%"
        )
  ) |> 
  filter(year == max(year)) |> 
  select(KPI_admin) |> 
  str_flatten()
